---
title: "Tidy HDDM Chains"
output: html_document
---

### Set up

This code converts a messy CSV containing the mcmc chains from the HDDM to a tidy data frame for analysis and visulaiztion. 

```{r}
read_path <- "02_analysis/02_scripts/hddm_analysis/"
library(here); library(tidyverse)
source(here(read_path, "code/hddm_helpers.R"))
```

### Read in chains from any saved model files that have 'mcmc' in file name

```{r}
files_to_read <- list.files(here(read_path, "data/raw_chains"), pattern = ".csv")

read_fun <- function(filename, read_path) {
  read_csv(file = here(read_path, "data/raw_chains", filename)) %>% 
    mutate(model_name = str_remove(filename, ".csv") %>% 
             str_remove('neginhib-mcmc-'))
}

d_mcmc <- files_to_read %>% 
  map_df(read_fun, read_path = read_path) %>% 
  rename(sample_number = X1)
```

Rename and clean up the column names using our own helper function. 

```{r}
condition_names <- c("intercept", "implicature", "inhib", 
                     "negative", "positive", "unambiguous", "control")

names(d_mcmc) <- names(d_mcmc) %>% 
  purrr::map(process_condition_name, condition_names, df_type = "within") %>% 
  as.character() %>% 
  str_to_lower() %>% 
  str_replace(pattern = "\\.", replacement = "_") %>% 
  str_remove(pattern = "_trans")

# one off processing of cdm model name
d_mcmc <- d_mcmc %>% 
  mutate(model_name = ifelse(model_name == "cdm-kids-pinned-ndt", 
                             "pinned-ndt-cdm-kids",
                             model_name))
```

### Tidy model traces

Gather parameters and create variable to track group vs. individual-level parameters. 

```{r}
d_mcmc_tidy <- d_mcmc %>% 
  separate(col = model_name, into = c("model_type", "experiment"), sep = '-ndt-') %>% 
  gather(key = param_name, value = estimate, -sample_number, -model_type, -experiment) %>% 
  mutate(param_level = ifelse(str_detect(param_name, "subj"), "individual", "group")) 
```

Create separate data frames for group and individual ss chains and separate multiple information types that are stored in the parameter name variable.

```{r}
# group-level 
d_mcmc_group <- d_mcmc_tidy %>% filter(param_level == "group")

d_mcmc_group %>%
  mutate(param_name = case_when(
    param_name == "t" ~ "t_group_map",
    param_name == "t_std" ~ "t_group_std",
    str_detect(param_name, "std") ~ param_name, 
    TRUE ~ str_c(param_name, "map", sep = "_")
  )) %>% 
  separate(param_name, into = c("param_type", "condition", "statistic"), sep = "_") %>% 
  mutate(subid = NA) -> d_mcmc_group

# individual-level 
d_mcmc_ss <- d_mcmc_tidy %>% filter(param_level == "individual")

## Note that this next step will produce warnings for the separate step since there
## aren't conditions assoicated with the individual level intercepts for each 
## hddm parameter (but this is OK! we only need this variable to bind the group
## and individual estimates in the next chunk)

d_mcmc_ss %>% 
  mutate(subid = str_extract(param_name, "_subj_[:digit:]+") %>% str_extract("[:digit:]+"),
         param_name = str_remove(param_name, "_subj_[:digit:]+")) %>% 
  separate(param_name, into = c("param_type", "condition"), sep = "_") %>% 
  mutate(statistic = "map") -> d_mcmc_ss
```

Pull everything back together and add some relevant variables.

```{r}
d_mcmc_final <- bind_rows(d_mcmc_group, d_mcmc_ss)

d_mcmc_final %>% 
  mutate(model_type = "within-subjects",
         game = case_when(
           condition == "intercept" | condition == "negative" ~ "negation_game",
           condition == "inhib" | condition == "control" ~ "inhibition_game",
           condition == "implicature" | condition == "unambiguous" ~ "implicature_game",
           TRUE ~ "NA"),
         plot_order = case_when(
           game == "negation_game" ~ 3,
           game == "inhibition_game" ~ 1,
           game == "implicature_game" ~ 2),
         param_type = case_when(
           param_type == "a" ~ "boundary",
           param_type == "t" ~ "non-decision time",
           param_type == "v" ~ "drift",
           param_type == "z" ~ "bias",
           TRUE ~ "NA"),
         condition_clean = ifelse(condition == "intercept", "positive", condition)) -> d_mcmc_final
```

Compute parameter values for each condition (i.e., not relative to intercept).

```{r}
intercept <- d_mcmc_final %>% 
  filter(condition == "intercept", param_level == "group", statistic == "map") %>% 
  select(sample_number, estimate, param_type, experiment) %>% 
  rename(intercept_estimate = estimate)

d_mcmc_final %>% 
  filter(statistic == "map") %>%
  dplyr::left_join(., intercept) %>% 
  mutate(group_param_estimate = ifelse(condition == "intercept", intercept_estimate, 
                                       intercept_estimate + estimate)) -> d_mcmc_final
```

### Save tidy model traces

```{r}
write_feather(d_mcmc_final, here(read_path,"data/tidy_chains/neginhib-mcmc-tidy-all.feather"))
```
