---
title: "Diffusion Models of neginhib game"
author: "Erica Yoon"
date: "Aug 5 2015"
output: html_document
---
`r library(knitr)`
`r opts_chunk$set(message=FALSE, warning=FALSE)`

## Data Loading

Load required Libraries
```{r}
rm(list=ls())
library(ggplot2)
library(dplyr)
library(tidyr)
library(magrittr)
library(directlabels)
library(RWiener)
```

Fixing up the wiener_plot function to deal with missing data
```{r}
wiener.plot <- function (dat) 
{
    rt = as.double(dat$q)
    rc = as.numeric(as.factor(dat$resp))
    dpos = tryCatch(density(rt[rc == 1], from = 0),error=function(e) NA)
    dneg = tryCatch(density(rt[rc == 2], from = 0),error=function(e) NA)
    maxt = max(pretty(max(rt)))
    
    maxd <- NA
    if(is.na(dpos[1])){
      maxd <- max(dneg$y)
      } else if(is.na(dneg[1])){
        maxd <- max(dpos$y)
        } else {
          maxd <- max(dpos$y, dneg$y)
          }
    
    par(mar = c(0, 5, 0, 0), mfcol = c(2, 1), ask = FALSE)
    plot(dpos, xlim = c(0, maxt), ylim = c(0, maxd), las = 2, 
        lwd = 2, col = "green3", main = "", ylab = "", ask = FALSE)
    rug(rt[rc == 1], col = "green3")
    mtext("Density of positive responses", side = 2, line = 4, 
        cex = 0.8)
    plot(dneg, xlim = c(0, maxt), ylim = c(maxd, 0), las = 2, 
        lwd = 2, col = "red", main = "", ylab = "", ask = FALSE)
    mtext("Density of negative responses", side = 2, line = 4, 
        cex = 0.8)
    rug(rt[rc == 2], col = "red", side = 3)
}
```

Read in adult data
```{r,fig.height=3,fig.width=4.5}
data <- read.csv("~/Documents/Research/neg_inhib/neginhib_GIT/long_data/long_data_mturk.csv") %>%
  mutate(WorkerId = subid) %>%
  mutate(cond = list) %>%
  mutate(trialnum = trial.num) %>%
  mutate(correct = response) %>%
  mutate(trialtype = trial.type) %>%
  select(WorkerId, cond, trialnum, correct, game, trialtype, rt) %>%
  group_by(WorkerId, trialnum) %>%
  mutate(side = if(((trialtype == "positive") || (trialtype == "unambiguous") || (trialtype == "control")) 
                  & (correct == "Y")) "more"
         else if(((trialtype == "positive") || (trialtype == "unambiguous") || (trialtype == "control"))
                  & (correct == "N")) "less"
         else if(((trialtype == "negative") || (trialtype == "implicature") || (trialtype == "inhib")) 
                  & (correct == "N")) "more"
         else "less") %>%
  mutate(resp = as.character(factor(side,levels=c("more","less"),
                                    labels=c("upper","lower")))) %>%
  mutate(q = rt/1000) %>%
  group_by() %>%
  select(q,trialtype,resp) %>%
  filter(q > 0) %>% # filtering the mysterious neg rt...
  filter(log(q) < mean(log(q)) + 2 * sd(log(q)),
         log(q) > mean(log(q)) - 2 * sd(log(q))) 

positive.data <- filter(data,trialtype == "positive") %>%
  select(q,resp)
wiener.plot(positive.data)

negative.data <- filter(data,trialtype == "negative") %>%
  select(q,resp) %>%
  as.data.frame
wiener.plot(negative.data)

unambiguous.data <- filter(data,trialtype == "unambiguous") %>%
  select(q,resp) %>%
  as.data.frame
wiener.plot(unambiguous.data)

implicature.data <- filter(data,trialtype == "implicature") %>%
  select(q,resp) %>%
  as.data.frame
wiener.plot(implicature.data)

inhib.control.data <- filter(data,trialtype == "control") %>%
  select(q,resp) %>%
  as.data.frame
wiener.plot(inhib.control.data)

inhib.data <- filter(data,trialtype == "inhib") %>%
  select(q,resp) %>%
  as.data.frame
wiener.plot(inhib.data)
```

Compute parameters for each condition separately
```{r}
optim.positive <- optim(c(1, .1, .1, 1), wiener_deviance, 
                           dat=positive.data, method="Nelder-Mead")
optim.negative <- optim(c(1, .1, .1, 1), wiener_deviance, 
                           dat=negative.data, method="Nelder-Mead")
optim.unambiguous <- optim(c(1, .1, .1, 1), wiener_deviance, 
                           dat=unambiguous.data, method="Nelder-Mead")
optim.implicature <- optim(c(1, .1, .1, 1), wiener_deviance, 
                           dat=implicature.data, method="Nelder-Mead")
optim.inhib.control <- optim(c(1, .1, .1, 1), wiener_deviance, 
                           dat=inhib.control.data, method="Nelder-Mead")
optim.inhib <- optim(c(1, .1, .1, 1), wiener_deviance, 
                           dat=inhib.data, method="Nelder-Mead")

indiv.pars <- as.data.frame(rbind(optim.positive$par,
                                  optim.negative$par,
                                  optim.unambiguous$par,
                                  optim.implicature$par,
                                  optim.inhib.control$par,
                                  optim.inhib$par))
names(indiv.pars) <- c("Separation","Non.Decision","Bias","Drift")
indiv.pars$Condition <- c("Control", "Target", "Control", "Target","Control", "Target")
indiv.pars$Game<- c("neg.game","neg.game","imp.game","imp.game", "inhib.game","inhib.game")
print(indiv.pars)
```

Pin parameters for item.num together
```{r}
# Function for tying parameters together across conditions
many_drifts <- function(x, datlist) {
  l = 0
  for (c in 1:length(datlist)) {
    l = l + wiener_deviance(x[c(1, 2, 3, c+3)], datlist[[c]])
  }
  
  return(l)
}

datlist.cond.neg <- list(positive.data, negative.data)
datlist.cond.imp <- list(unambiguous.data, implicature.data)
datlist.cond.inhib <- list(inhib.control.data, inhib.data)

# use nlm to estimate parameters
optim.cond.neg <- optim(p=c(1, .1, .1, 1, 1), many_drifts, 
                   dat=datlist.cond.neg,method="Nelder-Mead")
optim.cond.imp <- optim(p=c(1, .1, .1, 1, 1), many_drifts, 
                   dat=datlist.cond.imp,method="Nelder-Mead")
optim.cond.inhib <- optim(p=c(1, .1, .1, 1, 1), many_drifts, 
                   dat=datlist.cond.inhib,method="Nelder-Mead")

joint.pars <- as.data.frame(rbind(optim.cond.neg$par,optim.cond.imp$par, optim.cond.inhib$par))
names(joint.pars) <- c("Separation","Non.Decision","Bias",
                       "Control", "Target")
joint.pars <- gather(joint.pars,Condition,Drift,Control:Target)
joint.pars$Game <- c("neg.game", "imp.game", "inhib.game","neg.game", "imp.game", "inhib.game")
joint.pars %<>% select(Separation,Non.Decision,Bias,
                       Drift,Condition,Game) %>%
  arrange(Condition,Game)

print(joint.pars)
```

Pin non-decision time for a group, pin boundaries and bias within a condition
```{r}
# Function for tying parameters together across conditions
multi.loss.func <- function(x, datmat) {
  l = 0
  num.conds <- length(datmat)
  num.types <- length(datmat[[1]])
  
  # model takes (sep, non-decision, bias, drift)
  
  # x has (non-decision, sep-1, bias-1, drift-11, drift-12,
  #                      sep-2, bias-2, drift-21, drift-22)

  for (cond in 1:num.conds) {
    for(type in 1:num.types){

      l = l + wiener_deviance(x[c(2+(cond-1)*(2+num.types), 1, 
                                  3+(cond-1)*(2+num.types), 
                                  3+(cond-1)*(2+num.types)+type)], 
                              datmat[[cond]][[type]]) # fixme: need to adjust this to look at 3 instead of 2 games?
    }
  }
  
  return(l)
}
```

neg vs. implicature
```{r}
#Function for reconstructing the parameter matrix
make.par.mat <- function(optim.output) {
  pars <- as.data.frame(t(optim.output$par))
  names(pars) <- c("NonDecision","Separation.control","Bias.control",
                   "Drift.Control.control","Drift.Inference.control",
                   "Separation.target","Bias.target",
                   "Drift.Control.target","Drift.Inference.target")

  par.mat <- expand.grid(Condition = c("control", "target"),
                         Game = c("neg.game", "imp.game")) #fixme to include inhib game
  
  par.mat$NonDecision <- pars[,"NonDecision"]
  par.mat$Separation <- rep(c(pars[,"Separation.control"],
                              pars[,"Separation.target"]))
  par.mat$Bias <- rep(c(pars[,"Bias.control"],
                        pars[,"Bias.target"]))
  par.mat$Drift <- c(pars[,"Drift.Control.control"],
                     pars[,"Drift.Control.target"],
                     pars[,"Drift.Inference.control"],
                     pars[,"Drift.Inference.target"])
  
  return(par.mat)
}

datlist.control <- list(positive.data, unambiguous.data) #fixme to include inhib game
datlist.target <- list(negative.data, implicature.data) #fixme to include inhib game
datmat <- list(datlist.control,datlist.target)


  # x has (non-decision, sep-1, bias-1, drift-11, drift-12,
  #                      sep-2, bias-2, drift-21, drift-22)

optim.adult <- optim(p=c(.1, 1,.5, 1, -1, 1, .5, 1, -1), multi.loss.func, 
                   dat=datmat,method="BFGS")

adult.pars <- make.par.mat(optim.adult)

print(adult.pars)
```

neg vs. inhib
```{r}
#Function for reconstructing the parameter matrix
make.par.mat <- function(optim.output) {
  pars <- as.data.frame(t(optim.output$par))
  names(pars) <- c("NonDecision","Separation.control","Bias.control",
                   "Drift.Control.control","Drift.Inference.control",
                   "Separation.target","Bias.target",
                   "Drift.Control.target","Drift.Inference.target")

  par.mat <- expand.grid(Condition = c("control", "target"),
                         Game = c("neg.game", "inhib.game")) #fixme to include inhib game
  
  par.mat$NonDecision <- pars[,"NonDecision"]
  par.mat$Separation <- rep(c(pars[,"Separation.control"],
                              pars[,"Separation.target"]))
  par.mat$Bias <- rep(c(pars[,"Bias.control"],
                        pars[,"Bias.target"]))
  par.mat$Drift <- c(pars[,"Drift.Control.control"],
                     pars[,"Drift.Control.target"],
                     pars[,"Drift.Inference.control"],
                     pars[,"Drift.Inference.target"])
  
  return(par.mat)
}

datlist.control <- list(positive.data, inhib.control.data) #fixme to include inhib game
datlist.target <- list(negative.data, inhib.data) #fixme to include inhib game
datmat <- list(datlist.control,datlist.target)


  # x has (non-decision, sep-1, bias-1, drift-11, drift-12,
  #                      sep-2, bias-2, drift-21, drift-22)

optim.adult <- optim(p=c(.1, 1,.5, 1, -1, 1, .5, 1, -1), multi.loss.func, 
                   dat=datmat,method="BFGS")

adult.pars <- make.par.mat(optim.adult)

print(adult.pars)
```

inhib vs. implicature
```{r}
#Function for reconstructing the parameter matrix
make.par.mat <- function(optim.output) {
  pars <- as.data.frame(t(optim.output$par))
  names(pars) <- c("NonDecision","Separation.control","Bias.control",
                   "Drift.Control.control","Drift.Inference.control",
                   "Separation.target","Bias.target",
                   "Drift.Control.target","Drift.Inference.target")

  par.mat <- expand.grid(Condition = c("control", "target"),
                         Game = c("inhib.game", "imp.game")) #fixme to include inhib game
  
  par.mat$NonDecision <- pars[,"NonDecision"]
  par.mat$Separation <- rep(c(pars[,"Separation.control"],
                              pars[,"Separation.target"]))
  par.mat$Bias <- rep(c(pars[,"Bias.control"],
                        pars[,"Bias.target"]))
  par.mat$Drift <- c(pars[,"Drift.Control.control"],
                     pars[,"Drift.Control.target"],
                     pars[,"Drift.Inference.control"],
                     pars[,"Drift.Inference.target"])
  
  return(par.mat)
}

datlist.control <- list(inhib.control.data, unambiguous.data) #fixme to include inhib game
datlist.target <- list(inhib.data, implicature.data) #fixme to include inhib game
datmat <- list(datlist.control,datlist.target)


  # x has (non-decision, sep-1, bias-1, drift-11, drift-12,
  #                      sep-2, bias-2, drift-21, drift-22)

optim.adult <- optim(p=c(.1, 1,.5, 1, -1, 1, .5, 1, -1), multi.loss.func, 
                   dat=datmat,method="BFGS")

adult.pars <- make.par.mat(optim.adult)

print(adult.pars)
```